Say Cheese! A Snapshot of Canadian Family Demographics

### 2022-03-21 outputs/paper/paper.Rmd
update
supp survey

The supplementary survey can be found at https://forms.gle/jun4vZaAh247442s5 .

>>>>

The supplementary survey can be found at https://forms.gle/jun4vZaAh247442s5.

```{r supp questions fig, echo=FALSE, fig.cap="Supplementary Survey Questions", out.width = '100%'}
knitr::include_graphics(here::here("inputs/data/survey_1.png"))
knitr::include_graphics(here::here("inputs/data/survey_2.png"))
knitr::include_graphics(here::here("inputs/data/survey_3.png"))
knitr::include_graphics(here::here("inputs/data/survey_4.png"))
knitr::include_graphics(here::here("inputs/data/survey_5.png"))
```
